Block bootstrap consistency\\under weak assumptions

### 2016-09-27 Paper.tex
[#27] Make very small wording changes in the paper

The assumption on the dispersion of the individual means,
$(\mu_{nt} - \bar\mu_n)^2$, is the same as \citepos{GoW:02} and
\citepos{GoJ:03} under their additional requirement that the
expected block length be $o(\sqrt{n})$. When
the blocks are larger than $o(\sqrt{n})$, a case that \citet{GoW:02}
and \citet{GoJ:03} do not consider, the dispersion must be smaller
than they require.
To see these implications of this assumption, it is helpful to
consider a simple example: a stochastic process with a single break of
size $\Delta_n$ at time $T_n$:
\begin{equation*}
\mu_{nt} =
\begin{cases}
  \mu & \text{if } t \leq T_n \\
  \mu + \Delta_n & \text{otherwise}.
\end{cases}
\end{equation*}
A small amount of algebra gives the relationship,
\begin{equation*}
  \sum_{t=1}^n (\mu_{nt} - \bar \mu_n)^2
  = T_n (n - T_n) \Delta_n^2 / n \equiv D_n;
\end{equation*}
we have defined $D_n$ to minimize notation in the subsequent
discussion.  For the Moving and Circular Block Bootstraps,
Theorem~\ref{T1}'s Assumption 2 holds if $D_n = o(n / M_n^2)$, and for
the same relationship must hold for the expected block length for the
Stationary Bootstrap. If $\Delta_n = \Delta_0$ and $T_n = \pi n$ for
some constants $\Delta_0$ and $\pi$ and for all $n$, then
$D_n \approx \Delta_0^2 \, c (1 - c) \, n$ and Assumption~2 fails to
hold. These values of $\Delta_n$ and $T_n$ describe a scenario where
there is a break large enough that its timing could be precisely
estimated \citep[as in][]{Bai:94}, but the break is ignored and the
bootstrap is applied to the entire dataset.

@@

  To show that $\sigma_n^{*2}$ converges, we can write
  \begin{multline}\label{eq:38}
    \sigma_n^{*2} - \sigma^2 = \E^*\Big\{ \sum_{j=1}^{J_n} (Z_{nj}^{*2} - Z_{nj}^{\prime*2}) \Big\}
    + \tfrac{1}{n} \sum_{\tau=0}^{n-1} \E^* \Big\{\sum_{j=1}^{J_n}
    \big( Z_{n}^{\prime}(\tau,M_{nj})^2 - \Em Z_{n}^{\prime}(\tau,M_{nj})^2 \big)\Big\} \\
    + \tfrac{1}{n} \sum_{\tau=0}^{n-1} \E^* \Big\{\sum_{j=1}^{J_n}
    \Em Z_{n}^{\prime}(\tau,M_{nj})^2  - \sigma^2\Big\}.
  \end{multline}
  Uniform integrability ensures that the convergence in~(\ref{eq:25})
  holds in $L_1$ and Lemma~\ref{L2} then implies that
  the first term in \eqref{eq:38} converges to zero in probability.
  Lemma~\ref{L5} proves that the second and third
  summation converge to zero in probability.

@@

\begin{proof}
  We will just present a proof of~\eqref{eq:30}. Uniform integrability
  of the first family of random variables is simply a restatement of
  that expression and unifom integrability of $Z_{nj}^{*2} n / M_{nj}$
  follows an abbreviated version of the proof of~\eqref{eq:30}.

>>>>

The assumption on the dispersion of the individual means,
$(\mu_{nt} - \bar\mu_n)^2$, is the same as \citepos{GoW:02} and
\citepos{GoJ:03} under their additional requirement that the
expected block length be $o(\sqrt{n})$. When
the blocks are larger than $o(\sqrt{n})$, a case that \citet{GoW:02}
and \citet{GoJ:03} do not consider, the dispersion must be smaller
than they require.
To see these implications of this assumption, it is helpful to
consider a simple example: a stochastic process with a single break of
size $\Delta_n$ at time $T_n$:
\begin{equation*}
\mu_{nt} =
\begin{cases}
  \mu & \text{if } t \leq T_n \\
  \mu + \Delta_n & \text{otherwise}.
\end{cases}
\end{equation*}
A small amount of algebra gives the relationship,
\begin{equation*}
  \sum_{t=1}^n (\mu_{nt} - \bar \mu_n)^2
  = T_n (n - T_n) \Delta_n^2 / n \equiv D_n;
\end{equation*}
we have introduced $D_n$ to minimize notation in the subsequent
discussion.  For the Moving and Circular Block Bootstraps,
Theorem~\ref{T1}'s Assumption 2 holds if $D_n = o(n / M_n^2)$, and for
the same relationship must hold for the expected block length for the
Stationary Bootstrap. If $\Delta_n = \Delta_0$ and $T_n = \pi n$ for
some constants $\Delta_0$ and $\pi$ and for all $n$, then
$D_n \approx \Delta_0^2 \, c (1 - c) \, n$ and Assumption~2 fails to
hold. These values of $\Delta_n$ and $T_n$ describe a scenario where
there is a break large enough that $\pi$ could be precisely
estimated \citep[as in][]{Bai:94}, but the break is ignored and the
bootstrap is applied to the entire dataset.

@@

  To show that $\sigma_n^{*2}$ converges, we can write
  \begin{multline}\label{eq:38}
    \sigma_n^{*2} - \sigma^2 = \E^*\Big\{ \sum_{j=1}^{J_n} (Z_{nj}^{*2} - Z_{nj}^{\prime*2}) \Big\}
    + \tfrac{1}{n} \sum_{\tau=0}^{n-1} \E^* \Big\{\sum_{j=1}^{J_n}
    \big( Z_{n}^{\prime}(\tau,M_{nj})^2 - \Em Z_{n}^{\prime}(\tau,M_{nj})^2 \big)\Big\} \\
    + \tfrac{1}{n} \sum_{\tau=0}^{n-1} \E^* \Big\{\sum_{j=1}^{J_n}
    \Em Z_{n}^{\prime}(\tau,M_{nj})^2  - \sigma^2\Big\}.
  \end{multline}
  Uniform integrability ensures that the convergence in~(\ref{eq:25})
  holds in $L_1$ as well and Lemma~\ref{L2} then implies that
  the first term in \eqref{eq:38} converges to zero in probability.
  Lemma~\ref{L5} proves that the second and third
  summation converge to zero in probability.

@@

\begin{proof}
  We will only present a proof of~\eqref{eq:30}. Uniform integrability
  of the first family of random variables is simply a restatement of
  that expression and unifom integrability of $Z_{nj}^{*2} n / M_{nj}$
  follows an abbreviated version of the proof of~\eqref{eq:30}.
